---
title: "Reproducible Research: Peer Assessment 1"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data
Reading the data using read.csv()
```{r, results='markup', warning=TRUE, message=TRUE, echo=TRUE}
if(!file.exists('activity.csv')){
    unzip('activity.zip')
}
Data <- read.csv('activity.csv')

```


## What is mean total number of steps taken per day?

Using as.Date function to change the data type of Date variable. And making the histogram.
```{r, results = "markup", echo=TRUE,message=TRUE }

Data$date <- as.Date(Data$date)
Daily <- rowsum(Data$steps,Data$date, na.rm = TRUE)
Daily <- data.frame(Daily)
names(Daily) <- "Steps"
hist(Daily$Steps, breaks = 20)
```
### Mean and Median 
Mean and Median of total steps per day is calculated:
```{r, results = "markup", echo=TRUE,message=TRUE }
mean(Daily$Steps)
median(Daily$Steps)
```
* Mean: 9354.2295
* Median:  10395
## What is the average daily activity pattern?

Using aggregate() function, the average daily activity is found.
```{r, results = "markup", echo=TRUE,message=TRUE }

Pattern <- aggregate(x=list(meanSteps=Data$steps), by=list(interval=Data$interval), FUN=mean, na.rm=TRUE)
```
### Making time series plot
Loading ggplot2 library to create the plot 
```{r, results = "markup", echo=TRUE,message=TRUE }
library(ggplot2)
ggplot(data = Pattern,aes(x = interval, y = meanSteps)) +
  geom_line()
```
### interval that contains max number of average steps
The interval of max number of average steps is found using which.max() function
```{r, results = "markup", echo=TRUE,message=TRUE }
Pattern[which.max(Pattern$meanSteps),]

```
Most step at 8:35

## Imputing missing values
Calculated and reported the total number of missing values in the dataset

```{r, results = "markup", echo=TRUE,message=TRUE }
Missing <- Data[which(is.na(Data$steps)),]
dim(Missing)
```
number of missing: 2304

Differences in activity patterns between weekdays and weekends
### Create a new variable with two levels
Using as.factor() function to add a new variable to separate the data into two groups
```{r, results = "markup", echo=TRUE,message=TRUE }
Data$wday <- as.factor(ifelse(weekdays(Data$date) %in% c("Saturday","Sunday"),"weekends","weekdays"))
```
### Plotting

```{r, results = "markup", echo=TRUE,message=TRUE }
pat_week <- aggregate( steps ~ interval + wday, data = Data, mean )
ggplot(pat_week,aes(interval, steps))+
geom_line()+
facet_grid(wday ~ .) +
xlab("5-minute interval") + 
ylab("avarage number of steps")
```